---
title: "Simple Linear Regression"
author: "Sasha Ajay Malkani"
date: "2025-05-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simple Linear Regression

# Importing the dataset
```{r importing the dataset}
dataset = read.csv('Salary_Data.csv')
print('Salary_Data.csv')
```

## Splitting the dataset into the Training set and Test set

You can also embed plots, for example:

```{r Splitting the dataset into the training set and test set}
library(caTools)
set.seed(123)
split = sample.split(dataset$Salary, SplitRatio = 2/3)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)

print(training_set)
print(test_set)
```
## Fitting Simple Linear Regression to the Training set

```{r Fitting Simple Linear Regression to the Training set}

regressor = lm(formula = Salary ~ YearsExperience, 
               data = training_set)

summary(regressor)

```

## Predicting the Test set results

```{r Predicting the Test set results}

y_pred = predict(regressor, newdata = test_set)

y_pred

```

## Visualising the Training set results

```{r Visualising the Training set results}
# install.packages('ggplot2')
library(ggplot2)

ggplot() +
  geom_point(aes(x = training_set$YearsExperience, y = training_set$Salary),
             colour = 'red') +
  geom_line(aes(x = training_set$YearsExperience, y = predict(regressor, newdata = training_set)),
            colour = 'blue') +
  ggtitle('Salary vs Experience (Training set)') +
  xlab('Years of Experience') +
  ylab('Salary')



```

## Visualising the Test set results

```{r Visualising the Test set results}
# install.packages('ggplot2')
library(ggplot2)

ggplot() +
  geom_point(aes(x = test_set$YearsExperience, y = test_set$Salary),
             colour = 'red') +
  geom_line(aes(x = training_set$YearsExperience, y = predict(regressor, newdata = training_set)),
            colour = 'blue') +
  ggtitle('Salary vs Experience (Test set)') +
  xlab('Years of Experience') +
  ylab('Salary')

```








Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
