---
title: "Decision Tree Classification (with decision tree plot)"
author: "Sasha Ajay Malkani"
date: "2025-06-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  Importing the dataset

```{r Importing the dataset}
dataset = read.csv('Social_Network_Ads.csv')
head(dataset)
dataset = dataset[3:5]
head(dataset)

```

## Encoding the target feature as factor

```{r Encoding the target feature as factor}
dataset$Purchased = factor(dataset$Purchased, levels = c(0, 1))

```

##  Splitting the dataset into the Training set and Test set

```{r Splitting the dataset into the Training set and Test set}
# install.packages('caTools')
library(caTools)
set.seed(123)
split = sample.split(dataset$Purchased, SplitRatio = 0.75)
training_set = subset(dataset, split == TRUE)
head(training_set)
test_set = subset(dataset, split == FALSE)
head(test_set)

```


##  Fitting Decision Tree to the Training set

```{r Fitting Decision Tree to the Training set}
# install.packages('rpart')
library(rpart)
classifier = rpart(formula = Purchased ~ .,
                   data = training_set)
summary(classifier)

```

## Predicting the Test set results

```{r Predicting the Test set results}
y_pred = predict(classifier, newdata = test_set[-3], type = 'class')
y_pred

```

##  Making the Confusion Matrix

```{r Making the Confusion Matrix}
cm = table(test_set[, 3], y_pred)
cm

```

## Accuracy

```{r Accuracy}
Accuracy = (56 + 30)/(56 + 30 + 6 + 8)
Accuracy

```


## Plotting the decision tree

```{r Plotting the decision tree}
plot(classifier)
text(classifier)

```





















Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
