---
title: "Natural Language Processing (NLP)"
author: "Sasha Ajay Malkani"
date: "2025-06-28"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing the dataset

```{r Importing the dataset}
dataset_original = read.delim("Restaurant_Reviews.tsv", quote = "", stringsAsFactors = FALSE)
head(dataset_original)

```

## Cleaning the texts

```{r Cleaning the texts}
# install.packages('tm')
# install.packages('SnowballC')
library(tm)
library(SnowballC)
corpus = VCorpus(VectorSource(dataset_original$Review))
corpus = tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, removeNumbers)
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, removeWords, stopwords())
corpus = tm_map(corpus, stemDocument)
corpus = tm_map(corpus, stripWhitespace)

```

## Creating the Bag of Words model

```{r Creating the Bag of Words model}
dtm = DocumentTermMatrix(corpus)
dtm = removeSparseTerms(dtm, 0.999)
dataset = as.data.frame(as.matrix(dtm))
dataset$Liked = dataset_original$Liked

```

## Encoding the target feature as factor

```{r Encoding the target feature as factor}
dataset$Liked = factor(dataset$Liked, levels = c(0, 1))

```

## Splitting the dataset into the Training set and Test set

```{r Splitting the dataset into the Training set and Test set}
# install.packages('caTools')
library(caTools)
set.seed(123)
split = sample.split(dataset$Liked, SplitRatio = 0.80)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)

```

## Fitting Random Forest classification to the Training set

```{r Fitting Random Forest classification to the Training set}
# install.packages('randomForest')
library(randomForest)
classifier = randomForest(x = training_set[-692], 
                          y = training_set$Liked, 
                          ntree = 10)

```


## Predicting the Test set results

```{r Predicting the Test set RF results}
y_pred = predict(classifier, newdata = test_set[-692])
y_pred

```

## Making the Confusion Matrix

```{r Making the Confusion Matrix for RF}
cm = table(test_set[, 692], y_pred)
cm

```

## Performance Metrics

```{r Metrics RF}
accuracy <- sum(diag(cm)) / sum(cm)
print(paste("Accuracy:", accuracy))
precision <- cm[2, 2] / sum(cm[2, ])
print(paste("Precision:", precision))
recall <- cm[2, 2] / sum(cm[, 2])
print(paste("Recall:", recall))
f1_score <- 2 * (precision * recall) / (precision + recall)
print(paste("F1 Score:", f1_score))

```

## Fitting Logistic Regression to the Training set

```{r Fitting Logistic Regression to the Training set}
classifier = glm(formula = Liked ~ .,
                 family = binomial,
                 data = training_set)

```


## Predicting the Test set results

```{r Predicting the Test set LR results}
prob_pred = predict(classifier, type = 'response', newdata = test_set[-692])
print(prob_pred)
y_pred = ifelse(prob_pred > 0.5, 1, 0)
print(y_pred)

```

## Making the Confusion Matrix 

```{r Making the Confusion Matrix for LR}
cm = table(test_set[, 692], y_pred)
cm

```

## Performance Metrics

```{r Metrics LR}

accuracy <- sum(diag(cm)) / sum(cm)
print(paste("Accuracy:", accuracy))
precision <- cm[2, 2] / sum(cm[2, ])
print(paste("Precision:", precision))
recall <- cm[2, 2] / sum(cm[, 2])
print(paste("Recall:", recall))
f1_score <- 2 * (precision * recall) / (precision + recall)
print(paste("F1 Score:", f1_score))

```

## Fitting K - Nearest Neighbours (KNN) to the Training set

```{r Fitting KNN to the Training set}
library(class)
y_pred = knn(train = training_set[, -692],
             test = test_set[, -692],
             cl = training_set[, 692],
             k = 5,
             prob = TRUE)

```

## Making the Confusion Matrix 

```{r Making the Confusion Matrix for KNN}
cm = table(test_set[, 692], y_pred)
cm

```

## Performance Metrics

```{r Metrics KNN}

accuracy <- sum(diag(cm)) / sum(cm)
print(paste("Accuracy:", accuracy))
precision <- cm[2, 2] / sum(cm[2, ])
print(paste("Precision:", precision))
recall <- cm[2, 2] / sum(cm[, 2])
print(paste("Recall:", recall))
f1_score <- 2 * (precision * recall) / (precision + recall)
print(paste("F1 Score:", f1_score))

```

## Fitting Linear Support Vector Machines (SVM) to the Training set

```{r Fitting Support Vector Machines (SVM) to the Training set}
# install.packages('e1071')
library(e1071)

classifier = svm(formula = Liked ~ .,
                 data = training_set,
                 type = 'C-classification',
                 kernel = 'linear')

```

## Predicting the Test set results

```{r Predicting the Test set results SVM}
y_pred = predict(classifier, newdata = test_set[-692])
y_pred

```

## Making the Confusion Matrix

```{r Making the Confusion Matrix SVM}
cm = table(test_set[, 692], y_pred)
cm

```

## Performance Metrics

```{r Metrics Linear SVM}

accuracy <- sum(diag(cm)) / sum(cm)
print(paste("Accuracy:", accuracy))
precision <- cm[2, 2] / sum(cm[2, ])
print(paste("Precision:", precision))
recall <- cm[2, 2] / sum(cm[, 2])
print(paste("Recall:", recall))
f1_score <- 2 * (precision * recall) / (precision + recall)
print(paste("F1 Score:", f1_score))

```

## Fitting Kernel Support Vector Machines (SVM) to the Training set

```{r Fitting Support Vector Machines (Kernel SVM) to the Training set}
# install.packages("e1071")
library(e1071)

classifier = svm(formula = Liked ~ .,
                 data = training_set,
                 type = 'C-classification',
                 kernel = 'radial')
```

## Predicting the Test set results

```{r Predicting the Test set results Kernel SVM}
y_pred = predict(classifier, newdata = test_set[-692])
y_pred

```

## Making the Confusion Matrix

```{r Making the Confusion Matrix Kernel SVM}
cm = table(test_set[, 692], y_pred)
cm

```

## Performance Metrics

```{r Metrics Kernel SVM}

accuracy <- sum(diag(cm)) / sum(cm)
print(paste("Accuracy:", accuracy))
precision <- cm[2, 2] / sum(cm[2, ])
print(paste("Precision:", precision))
recall <- cm[2, 2] / sum(cm[, 2])
print(paste("Recall:", recall))
f1_score <- 2 * (precision * recall) / (precision + recall)
print(paste("F1 Score:", f1_score))

```

## Fitting Naive Bayes Model to the Training set

```{r Fitting Naive Bayes to the Training set}
# install.packages("e1071")
library(e1071)

classifier = naiveBayes(x = training_set[,-692],
                        y = training_set$Liked)
```

## Predicting the Test set results

```{r Predicting the Test set results Naive Bayes}
y_pred = predict(classifier, newdata = test_set[-692])
y_pred

```

## Making the Confusion Matrix

```{r Making the Confusion Matrix Naive Bayes}
cm = table(test_set[, 692], y_pred)
cm

```

## Performance Metrics

```{r Metrics Naive Bayes}

accuracy <- sum(diag(cm)) / sum(cm)
print(paste("Accuracy:", accuracy))
precision <- cm[2, 2] / sum(cm[2, ])
print(paste("Precision:", precision))
recall <- cm[2, 2] / sum(cm[, 2])
print(paste("Recall:", recall))
f1_score <- 2 * (precision * recall) / (precision + recall)
print(paste("F1 Score:", f1_score))

```


## Fitting Decision Tree Model to the Training set

```{r Fitting Decision Tree to the Training set}
# install.packages('rpart')
library(rpart)
classifier = rpart(formula = Liked ~ .,
                   data = training_set)
```

## Predicting the Test set results

```{r Predicting the Test set results Decision Tree}
y_pred = predict(classifier, newdata = test_set[-692], type = 'class')
y_pred

```

## Making the Confusion Matrix

```{r Making the Confusion Matrix Decision Tree}
cm = table(test_set[, 692], y_pred)
cm

```


## Performance Metrics

```{r Metrics Decision Tree}

accuracy <- sum(diag(cm)) / sum(cm)
print(paste("Accuracy:", accuracy))
precision <- cm[2, 2] / sum(cm[2, ])
print(paste("Precision:", precision))
recall <- cm[2, 2] / sum(cm[, 2])
print(paste("Recall:", recall))
f1_score <- 2 * (precision * recall) / (precision + recall)
print(paste("F1 Score:", f1_score))

```








Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
