---
title: "Reinforcement Learning - Upper Confidence Bound (UCB)"
author: "Sasha Ajay Malkani"
date: "2025-06-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing the dataset

```{r Importing the dataset}
dataset = read.csv('Ads_CTR_Optimisation.csv')
head(dataset)
```

## Implementing UCB Algorithm

```{r Implementing UCB Algorithm}
# Implementing UCB - Step 1
N = 10000
d = 10
ads_selected = integer()
numbers_of_selections = integer(d)
sums_of_rewards = integer(d)
total_reward = 0

# Implementing UCB - Step 2
for (n in 1:N) {
  max_upper_bound = 0
  ad = 0
  for(i in 1:d) {
    if (numbers_of_selections[i] > 0) {
      average_reward = sums_of_rewards[i] / numbers_of_selections[i]
      delta_i = sqrt(3/2 * log(n) / numbers_of_selections[i])
      upper_bound = average_reward + delta_i
    } else {
      upper_bound = 1e400
    }
    
    
# Implementing UCB - Step 3
    if (upper_bound > max_upper_bound) {
      max_upper_bound = upper_bound
      ad = i
    }
  }
  ads_selected = append(ads_selected, ad)
  numbers_of_selections[ad] = numbers_of_selections[ad] + 1
  reward = dataset[n, ad]
  sums_of_rewards[ad] = sums_of_rewards[ad] + reward
  total_reward = total_reward + reward
}

```

## Total reward

```{r Total reward}
total_reward

```

## Ads Selected (most popular Ad displayed more frequently)

```{r Ads Selected}
head(ads_selected, n = 100)
tail(ads_selected, n = 100)

```

## Visualising the results - Histogram

```{r Visualising the results - Histogram}
hist(ads_selected,
     col = 'blue',
     main = 'Histogram of ads selections',
     xlab = 'Ads',
     ylab = 'Number of times each ad was selected')

```

## Implementing Random Selection (for comparison with UCB Algorithm)

```{r }
N = 10000
d = 10
ads_selected = integer(0)
total_reward = 0
for (n in 1:N) {
  ad = sample(1:10, 1)
  ads_selected = append(ads_selected, ad)
  reward = dataset[n, ad]
  total_reward = total_reward + reward
}

```

## Total reward for Random Selection (for comparison with UCB Algorithm)

```{r Total reward random}
total_reward

```

## Ads Selected for Random Selection (most popular Ad displayed more frequently) (for comparison with UCB Algorithm)

```{r Ads Selected random}
head(ads_selected, n = 100)
tail(ads_selected, n = 100)

```


## Visualising the results for Random Selection (for comparison with UCB Algorithm)

```{r Visualising the results random}
hist(ads_selected,
     col = 'blue',
     main = 'Histogram of ads selections',
     xlab = 'Ads',
     ylab = 'Number of times each ad was selected')
```






Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
