---
title: "K-NN Classification"
author: "Sasha Ajay Malkani"
date: "2025-06-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing the dataset

```{r Importing the dataset}
dataset = read.csv('Social_Network_Ads.csv')
head(dataset)
dataset = dataset[3:5]
head(dataset)

```

## Encoding the target feature as factor

```{r Encoding the target feature as factor}
dataset$Purchased = factor(dataset$Purchased, levels = c(0, 1))

```


## Splitting the dataset into the Training set and Test set

```{r Splitting the dataset into the Training set and Test set}
# install.packages('caTools')
library(caTools)
set.seed(123)
split = sample.split(dataset$Purchased, SplitRatio = 0.75)
training_set = subset(dataset, split == TRUE)
head(training_set)
test_set = subset(dataset, split == FALSE)
head(test_set)

```

## Feature Scaling

```{r Feature Scaling}
training_set[-3] = scale(training_set[-3])
head(training_set)
test_set[-3] = scale(test_set[-3])
head(test_set)

```


## Fitting K-NN to the Training set and Predicting the Test set results

```{r Fitting K-NN to the Training set and Predicting the Test set results}
# install.packages("class")
library(class)
y_pred = knn(train = training_set[, -3], 
             test = test_set[, -3],
             cl = training_set[, 3],
             k = 5)
y_pred

```

## Making the Confusion Matrix

```{r Making the Confusion Matrix}
cm = table(test_set[, 3], y_pred)
cm
```

## KNN Model Accuracy

```{r KNN Model Accuracy}
Accuracy = (59 + 30)/(59 + 30 + 6 + 5)
Accuracy

```



## Visualising the Training set results

```{r Visualising the Training set results}
library(ElemStatLearn)
set = training_set
X1 = seq(min(set[, 1]) - 1, max(set[, 1]) + 1, by = 0.01)
X2 = seq(min(set[, 2]) - 1, max(set[, 2]) + 1, by = 0.01)
grid_set = expand.grid(X1, X2)
colnames(grid_set) = c('Age', 'EstimatedSalary')
y_grid = knn(train = training_set[, -3], 
             test = grid_set,
             cl = training_set[, 3],
             k = 5)
plot(set[, -3],
     main = 'KNN (Training set)',
     xlab = 'Age', ylab = 'Estimated Salary',
     xlim = range(X1), ylim = range(X2))
contour(X1, X2, matrix(as.numeric(y_grid), length(X1), length(X2)), add = TRUE)
points(grid_set, pch = '.', col = ifelse(y_grid == 1, 'dodgerblue', 'salmon'))
points(set, pch = 21, bg = ifelse(set[, 3] == 1, 'dodgerblue3', 'salmon3'))

```

## Visualising the Test set results

```{r Visualising the Test set results}
library(ElemStatLearn)
set = test_set
X1 = seq(min(set[, 1]) - 1, max(set[, 1]) + 1, by = 0.01)
X2 = seq(min(set[, 2]) - 1, max(set[, 2]) + 1, by = 0.01)
grid_set = expand.grid(X1, X2)
colnames(grid_set) = c('Age', 'EstimatedSalary')
y_grid = knn(train = training_set[, -3], 
             test = grid_set,
             cl = training_set[, 3],
             k = 5)
plot(set[, -3],
     main = 'KNN (Test set)',
     xlab = 'Age', ylab = 'Estimated Salary',
     xlim = range(X1), ylim = range(X2))
contour(X1, X2, matrix(as.numeric(y_grid), length(X1), length(X2)), add = TRUE)
points(grid_set, pch = '.', col = ifelse(y_grid == 1, 'dodgerblue', 'salmon'))
points(set, pch = 21, bg = ifelse(set[, 3] == 1, 'dodgerblue3', 'salmon3'))


```











Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
