---
title: "Polynomial Linear Regression"
author: "Sasha Ajay Malkani"
date: "2025-06-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing the Dataset


```{r Importing the Dataset}
dataset = read.csv('Position_Salaries.csv')
print(dataset)

```

## Reset the dataset

```{r Reset the dataset}

dataset = dataset[2:3]
print(dataset)

```

## Fitting Linear Regression to the dataset

```{r Fitting Linear Regression to the dataset}
lin_reg = lm(formula = Salary ~ .,
             data = dataset)

summary(lin_reg)

```

## Fitting Polynomial Regression to the dataset

```{r Fitting Polynomial Regression to the dataset}
dataset$Level2 = dataset$Level^2
dataset$Level3 = dataset$Level^3
dataset$Level4 = dataset$Level^4
poly_reg = lm(formula = Salary ~ .,
             data = dataset)

summary(poly_reg)

```

## Visualizing the Linear Regression results

```{r Visualizing the Linear Regression results}
# install.packages('ggplot2')
library(ggplot2)
ggplot() + 
  geom_point(aes(x = dataset$Level, y = dataset$Salary), 
             colour = 'red') +
  geom_line(aes(x = dataset$Level, y = predict(lin_reg, newdata = dataset)), 
             colour = 'blue') +
  ggtitle('Truth or Bluff (Linear Regression)') +
  xlab('Level') +
  ylab('Salary')

```


## Visualizing the Polynomial Regression results

```{r Visualizing the Polynomial Regression results}
ggplot() + 
  geom_point(aes(x = dataset$Level, y = dataset$Salary), 
             colour = 'red') +
  geom_line(aes(x = dataset$Level, y = predict(poly_reg, newdata = dataset)), 
            colour = 'blue') +
  ggtitle('Truth or Bluff (Polynomial Regression)') +
  xlab('Level') +
  ylab('Salary')

```

## Predicting a new result with Linear Regression

```{r Predicting a new result with Linear Regression}
y_pred = predict(lin_reg, data.frame(Level = 6.5))

print(y_pred)

```

## Predicting a new result with Polynomial Regression

```{r Predicting a new result with Polynomial Regression}
y_pred = predict(poly_reg, data.frame(Level = 6.5,
                                      Level2 = 6.5^2,
                                      Level3 = 6.5^3,
                                      Level4 = 6.5^4))

print(y_pred)

```





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
