---
title: "Multiple Linear Regression"
author: "Sasha Ajay Malkani"
date: "2025-05-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing the dataset

```{r Importing the dataset}
dataset = read.csv('50_Startups.csv')
# dataset = dataset[, 2:3]

head(dataset, 10)

```

## Encoding categorical data

```{r Encoding categorical data}

dataset$State = factor(dataset$State, 
                         levels = c('New York', 'California', 'Florida'), 
                         labels = c(1, 2, 3))

head(dataset, 10)

```

## Splitting the dataset into the Training set and Test set

```{r Splitting the dataset into the Training set and Test set}
# install.packages('caTools')
library(caTools)
set.seed(123)
split = sample.split(dataset$Profit, SplitRatio = 0.8)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)

print(training_set)
print(test_set)

```

## Fitting Multiple Linear Regression to the Training set

```{r Fitting Multiple Linear Regression to the Training set}
regressor = lm(formula = Profit ~ ., 
               data = training_set)

summary(regressor)

```

## Predicting the Test set results


```{r Predicting the Test set results}
y_pred = predict(regressor, newdata = test_set)

y_pred

```

## Real profits from test set to compare against predicted profits above

```{r Real profits from test set to compare against predicted profits above}

print(test_set[, 5])
```

# Building the optimal model using Backward Elimination (manual)

# 4 variable model

```{r 4 variable model}


regressor = lm(formula = Profit ~ R.D.Spend + Administration + Marketing.Spend + State, 
               data = dataset)

summary(regressor)
```

# 3 variable model

```{r 3 variable model}


regressor = lm(formula = Profit ~ R.D.Spend + Administration + Marketing.Spend, 
               data = dataset)

summary(regressor)
```

# 2 variable model - possibly the final model with marketing spend being marginally significant


```{r 2 variable model}


regressor = lm(formula = Profit ~ R.D.Spend + Marketing.Spend, 
               data = dataset)

summary(regressor)
```

# 1 variable model - simple linear regression with R & D spend being the single independent variable


```{r 1 variable model}


regressor = lm(formula = Profit ~ R.D.Spend, 
               data = dataset)

summary(regressor)
```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
