---
title: "Association Rules Learning - Apriori"
author: "Sasha Ajay Malkani"
date: "2025-06-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing the dataset

```{r Importing the dataset}
# install.packages("arules")
library(arules)
dataset = read.csv('Market_Basket_Optimisation.csv', header = FALSE)
dataset = read.transactions('Market_Basket_Optimisation.csv', sep = ',', rm.duplicates = TRUE)
summary(dataset)
itemFrequencyPlot(dataset, topN = 10)
```

## Training Apriori on the dataset (support = 0.003 & confidence = 0.4)

```{r Training Apriori on the dataset 1}
rules = apriori(data = dataset, parameter = list(support = 0.003, confidence = 0.4))

```

## Visualising the results (support = 0.003 & confidence = 0.4)

```{r Visualising the results 1}
inspect(sort(rules, by = 'lift')[1:10])
```

## Training Apriori on the dataset (support = 0.003 & confidence = 0.2)

```{r Training Apriori on the dataset 2}
rules = apriori(data = dataset, parameter = list(support = 0.003, confidence = 0.2))

```

## Visualising the results (support = 0.003 & confidence = 0.2)

```{r Visualising the results 2}
inspect(sort(rules, by = 'lift')[1:10])
```

## Training Apriori on the dataset (support = 0.004 & confidence = 0.2)

```{r Training Apriori on the dataset 3}
rules = apriori(data = dataset, parameter = list(support = 0.004, confidence = 0.2))

```

## Visualising the results (support = 0.004 & confidence = 0.2)

```{r Visualising the results 3}
inspect(sort(rules, by = 'lift')[1:10])
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
